### 2013-07-25 0_frontmatter/abstract.tex
updated Ian's abstract and acknowledgement

On the one hand, practical application for POLSAR data processing requires the establishment of discrimination measures
  which are to be scalar and statistically consistent.
On the other hand, these same scalar observable quantities need to be naturally representative for the high-dimensional POLSAR data.
At the same time, it is desirable to establish additive and homoskedastic models, which include several consistent measures of distance, for both SAR and POLSAR data, so that the benefits of homoskedastic statistical estimation framework can be studied and realized.

In this thesis, the statistical behavior of the determinant of POLSAR covariance matrix is explored.
Concurrently, the effects of homoskedasticity on (POL)SAR speckle filtering within the framework of computational and statistical estimation are also extensively studied.

As the result of these studies, the scalar statistical models for the determinant of POLSAR covariance matrix is proposed and validated.
This observable turns out to be very representative of the complex data as it generalizes the SAR intensity towards the multi-dimensional extension.
Similar to the model for SAR intensity, this generic model for POLSAR is shown to be both multiplicative and heteroskedastic.
Consequently, logarithmic transformation is applied onto these types of data converting them into additive and homoskedastic models.
From these models, several additive measures of distance are proposed for both SAR and POLSAR data.

There are several beneficial implications of the theory proposed in this thesis. 
Since the scalar and representative model for POLSAR generalize the traditional model for SAR intensity, its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
At the same time, the benefit of the homoskedastic models is multiple-folds.
For in-experienced researchers (like this author when he started this study),
  who attempt to process either SAR or POLSAR data using existing computation algorithms
  which most of the time expect an additive and homoskedastic input,
  this thesis proposes alternative and more familiar additive and homoskedastic models
    in place of the original ones which are multiplicative and heteroskedastic.
For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the (POL)SAR statistical estimation framework.

>>>>

On the one hand, practical applications for POLSAR data processing require the establishment of discrimination measures
  which are to be scalar and statistically consistent.
On the other hand, these same scalar observable quantities need to be naturally representative of the high-dimensional POLSAR data.
At the same time, it is desirable to establish additive and homoskedastic models, which include several consistent measures of distance, for both SAR and POLSAR data, so that the benefits of homoskedastic statistical estimation framework can be studied and realized.

In this thesis, the statistical behaviour of the determinant of POLSAR covariance matrix is explored.
Concurrently, the effects of homoskedasticity on (POL)SAR speckle filtering within the framework of computational and statistical estimation are also extensively studied.

As a result of these studies, the scalar statistical models for the determinant of POLSAR covariance matrix are proposed and validated.
This observable turns out to be very representative of the complex data as it generalizes the SAR intensity towards the multi-dimensional extension.
Similar to the model for SAR intensity, this generic model for POLSAR is shown to be both multiplicative and heteroskedastic.
Consequently, logarithmic transformation is applied onto these types of data converting them into additive and homoskedastic models.
From these models, several additive measures of distance are proposed for both SAR and POLSAR data.

There are several beneficial implications of the theory proposed in this thesis. 
Since the scalar and representative model for POLSAR generalizes the traditional model for SAR intensity, its main benefit is that it enables the adaptation of many existing SAR data processing techniques for POLSAR data.
Similarly, the homoskedastic model carries additional benefits.
For inexperienced researchers (such as this author when he began this research),
  who attempt to process either SAR or POLSAR data using existing computation algorithms
  which most of the time expect an additive and homoskedastic input,
  this thesis proposes alternative and more familiar additive and homoskedastic models. These replace
 the original ones which are multiplicative and heteroskedastic.
For more experienced researchers, besides the unified scalar statistical theory for both SAR and POLSAR, 
  this thesis also proposes several ways that homoskedastic data processing can be used to neutralize certain existing negative impacts of heteroskedasticity on the (POL)SAR statistical estimation framework.

### 2013-07-25 0_frontmatter/acknowledgement.tex
updated Ian's abstract and acknowledgement

Before anything, I would like to express my gratitude towards my family, specifically my wife, my parents and my kids,
  whose constant love and unconditional support I have greatly relied upon. 
Their immeasurable sacrifices together with their continous encouragement have always been the motivation for me to follow this academic pursuit.
%venture further. 
%It is ultimately to them that this work is dedicated.
They are the first and foremost people that this work is dedicated upon.

This thesis would also not have been possible without the patient and helpful guidance of Assoc. Prof. Ian McLoughlin and Assoc Prof. Nicholas Vun Chan Hua, 
	under whose supervision I am gratefully being under. 
The supervisors have been providing firm support, as well as spot-on guidance. 
During all the stages of my research work, 
	be it conceptualization or result analysis, be it writing, presentation or publishing ..
	their kind attention and wise advices command my utmost respect and admiration.

@@

Special thanks go to my friends and colleagues, whose friendship and companion have made the journey a truly enjoyable one. 
They include but not limited to: Brian Nguyen Quang Huy, Erwin Anggadjaja and Hamid Reza Sharifzadeh ...

Last but not least I would like to give my appreciations to all NTU staffs at PDCC, SCE and GSO whose quiet but continous supporting efforts played a very important role in any measure of success this dissertation may be associated with.

>>>>

Before anything, I would like to express my gratitude towards my family, specifically my wife, my parents and my kids,
  whose constant love and unconditional support I have greatly relied upon. 
Their immeasurable sacrifices together with their continuous encouragement have always been the motivation for me to follow this academic pursuit.
%venture further. 
%It is ultimately to them that this work is dedicated.
They are the first and foremost people that this work is dedicated upon.

This thesis would also not have been possible without the patient and helpful guidance of Professor Ian McLoughlin and Associate Professor Nicholas Vun Chan Hua, 
	under whose supervision I am gratefully under. 
The supervisors have provided firm support, as well as spot-on guidance. 
During all the stages of my research work, 
	be it conceptualization or result analysis, be it writing, presentation or publishing ..
	their kind attention and wise advice command my utmost respect and admiration.

@@

Special thanks go to my friends and colleagues, whose friendship and companionship have made the journey a truly enjoyable one. 
They include but are not limited to: Brian Nguyen Quang Huy, Erwin Anggadjaja and Hamid Reza Sharifzadeh ...

Last but not least I would like to give my appreciation to all NTU staff in PDCC, SCE and GSO whose quiet but continuous supporting efforts played a very important role in any measure of success this dissertation may be associated with.
